Extreme Value Statistics Draft 1

### 2022-03-24 Draft#1.Rmd
draft_changes

---
title: "Extreme Value Statistics Draft 1"
Dataset: Wind 
Group: 1
Name: Chaitanya Arora, Diandra Gramma 
output: html_document
---

## Introduction ##

@@

## Step 1: Basic Analysis of the data ##

1.1 The graphical representation of the 5 places we are analysing in this project

@@

1.2 The Basic plots to understand the graph better

@@

<<<<<<<<<< XY Plot >>>>>>>

@@

<< Box Plot >>

@@

@@

<<<<QQ Plot>>>

@@

<<<< GEV Plots >>>

@@

<<<<<Mean excess plot>>>>

@@

<<<<<<<<<<<<<<<<< bi-variate Analysis >>>>>>>>>>>>>>>>>>

@@

This is the line of best fit
```{r}
dates_new=as.Date(dates)
plot(dataset[,2],dataset[,1])
abline(lm(dataset[,2]~dataset[,1]))

@@

<<<<<<<<< Multivariate analysis >>>>>>>>

@@

1. Extremal Independence:

@@

<<<< Scatter plot diagram :>>>

@@

<<<<Marginal standardization based on the rank transform>>>

@@

<<<<Estimation of the extremal coefficient>>>>>

@@

<<<<Estimation of the coefficient of tail dependence>>>>

@@

<<<<<Modeling extremal dependence:>>>>>>>

@@

<<<<<<<<Conclusions>>>

>>>>

---
Title: "Extreme Value Statistics Draft 1"
Dataset: Wind 
Group: 1
Name: Chaitanya Arora, Diandra Gramma 
output: html_document
---

################# Introduction ####################

@@

<<<<<<<<<. Basic Analysis of the data >>>>>>>>>>>>

1 The graphical representation of the 5 places we are analysing in this project

@@

2. The Basic plots to understand the graph better

@@

3. <<<<<<<<<< XY Plot >>>>>>>

@@

4. <<<<< Box Plot >>>>>

@@

5. <<<<<< Dot plots >>>>>>

@@

6. <<<<<< QQ Plot >>>>>

@@

7. <<<<<< GEV Plots >>>>>>

@@

8. <<<<<<<<Mean excess plot>>>>>>

@@

<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<< bi-variate Analysis >>>>>>>>>>>>>>>>>>

@@

This is the line of best fit

9. <<<<<Line of best fit>>>>>

```{r}
dates_new=as.Date(dates)
plot(dataset[,2],dataset[,1])
abline(lm(dataset[,2]~dataset[,1]))

@@

<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<< Multivariate analysis >>>>>>>>

@@

Extremal Independence:

@@

10. <<<<<<<<<< Scatter plot diagram :>>>>>>>>>>

@@

11. <<<<<<<<<< Marginal standardization based on the rank transform >>>>>>>>

@@

12. <<<<<<<<< Estimation of the extremal coefficient >>>>>>>>>>>

@@

13. <<<<<<<<< Estimation of the coefficient of tail dependence >>>>>>

@@

14. <<<<< Modeling extremal dependence: >>>>>>>

@@

15. <<<<<<<< Conclusions >>>>>>>
